Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-03-01 paper.tex
test
diagram

\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{multirow}

@@

We propose an extension to G-PTM-D (Enhanced G-PTM-D) that addresses the long search times of the wide-mass search, and the limitations of the standard final narrow-mass search.
The wide-mass search is replaced by a notch search in the discovery phase, using notches centered at the monoisotopic mass differences introduced by known modifications.
This change improves the specificity and significantly decreases search time.
The final narrow-mass search is also replaced by a notch search, further increasing the number of confidently identified peptides.

@@

\begin{figure}
  \includegraphics{figureDifferentSearchModes.eps}
  \caption{Search Modes}
  \label{fgr:differentSearchModes}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{suppinfo}

>>>>

\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{multirow}
\usepackage{subcaption}

@@

We propose an enhancement to G-PTM-D, that addresses the long search times of the wide-mass search, and the limitations of the standard final narrow-mass search.
The wide-mass search is replaced by a notch search in the discovery phase, using notches centered at the monoisotopic mass differences introduced by known modifications.
This change improves the specificity and significantly decreases search time.
The final narrow-mass search is also replaced by a notch search, further increasing the number of confidently identified peptides.

@@

\begin{figure}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.5\linewidth}
  \includegraphics{figureDifferentSearchModes.eps}
  \caption{Search Modes}
  \label{fgr:differentSearchModes}
\end{subfigure}%
\begin{subfigure}[b]{.5\linewidth}
  \includegraphics[scale=0.5]{diagram.eps}
  \caption{Workflows}
  \label{fgr:diagram}
\end{subfigure}
\caption{A figure}\label{fig:1}
\end{figure}

@@

\begin{suppinfo}
